\problemname{Animal}
\noindent
In a grid with $R$ rows and $C$ columns, a wolf stands at cell $(1, 1)$ and a rabbit stands at cell $(R, C)$.
The wolf wants to move to cell $(R, C)$, and the rabbit wants to move to cell $(1, 1)$.
However, there is a problem: if their paths cross, the wolf will follow the rabbit and chase it.
Now we wonder, given the layout of the grid, can you find a path for both the rabbit and the wolf so that their paths do not cross each other?
The start and end cells ($(1, 1)$ and $(R, C)$) are not counted as part of the path.

\section*{Input}
The first line contains two integers: $R$ and $C$. In all test cases, it holds that $2 \leq R \cdot C \leq 2 \cdot 10^5$.

Then follows an $R \times C$ grid. Each cell is either ``\texttt{.}'' which means an empty cell, or ``\texttt{\#}'' which means an obstacle.

It is guaranteed that the cells (1,1) and (R,C) are empty.

\section*{Output}
Print \texttt{NO} if there are no two paths that meet the requirements of the task.

Otherwise, print a line with \texttt{YES}.
Then print a grid where you mark the rabbit's path with ``\texttt{K}'' and the wolf's path with ``\texttt{V}''.
Note that all obstacles must remain obstacles when you print the grid and that all empty cells that are not part of the paths must remain empty cells.
A path must be contiguous.

If you are using C++, it may be good to use \texttt{'\textbackslash{}n'} instead of \texttt{endl} to avoid risking Time Limit Exceeded on a working solution.

\section*{Scoring}
Your solution will be tested on a set of test groups, each worth a number of points. Each test group contains
a set of test cases. To get the points for a test group you need to solve all test cases in the test group.

\noindent
\begin{tabular}{| l | l | l |}
  \hline
  \textbf{Group} & \textbf{Points} & \textbf{Constraints} \\ \hline
  $1$   & $9$        & There are on obstacles. \\ \hline
  $2$   & $10$       & $R \cdot C \leq 10$  \\ \hline
  $3$   & $20$       & $R = 3$  \\ \hline
  $4$   & $25$       & $R \cdot C \leq 1000$, and there exist a solution where the wolf only walks down and right, and the rabbit only up and left. \\ \hline
  $5$   & $36$       & No additional constraints. \\ \hline
\end{tabular}

Note that some example cases are not valid in all test case groups.
